\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2018-10-12 paper/supporting_information.tex
updated supp fig caption per lucy's comments

\begin{figure}[b!]
\centering
\includegraphics[width=0.6\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.} The split
  violin plot reflects the same data as Figure~3A, presented here for
  comparison.  \textbf{B. Distributions of correlation between
    observed versus reconstructed activity by electrode, for Dataset
    2.}  The right-most split violin plot (``All'') reflects the same
  data as Figure~3B, presented here for comparison.  The ``Within''
  plot reflects the same analyses, but limited to models that were
  trained and tested on only one of the Dataset 2 experiments at a
  time.  The ``Across'' plot reflects the same analyses, but limited
  to models that were trained and tested on \textit{different} Dataset
  2 experiments.  All plots: the dark gray distributions denote
  across-subject correlations (model trained on all but one patient
  and tested on the held-out patient), and the medium gray
  distributions denote within-subject correlations (model trained on
  all but one electrode from one patient, and tested on the held-out
  electrode).  The horizontal bars denote $t$-tests between the
  corresponding distributions (after $z$-transforming the
  correlations), and the white numbers reflect the distribution means.
  The symbols denote the corresponding $p$-values of those statistical
  tests.}
\label{fig:supplemental_1}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (rightmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (rightmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location.}
\label{fig:supplemental_3}
\end{figure}

>>>>

\begin{figure}[b!]
\centering
\includegraphics[width=0.6\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.} The split
  violin plot reflects the same data as Figure~3A, presented here for
  comparison.  \textbf{B. Distributions of correlation between
    observed versus reconstructed activity by electrode, for Dataset
    2.}  The left-most split violin plot (``Within'') reflects the
  same data as Figure~3B, presented here for comparison.  The
  ``Across'' plot reflects the same analyses, but limited to models
  that were trained and tested on \textit{different} Dataset 2
  experiments.  The ``All'' plot reflects the same analyses, but
  including models that were trained and tested on both of the Dataset
  2 experiments.  All plots: the dark gray distributions denote
  across-subject correlations (model trained on all but one patient
  and tested on the held-out patient), and the medium gray
  distributions denote within-subject correlations (model trained on
  all but one electrode from one patient, and tested on the held-out
  electrode).  The horizontal bars denote $t$-tests between the
  corresponding distributions (after $z$-transforming the
  correlations), and the white numbers reflect the distribution means.
  The symbols denote the corresponding $p$-values of those statistical
  tests.}
\label{fig:supplemental_1}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location.}
\label{fig:supplemental_3}
\end{figure}
